CompDec - Detect the Compression Algorithm of File Fragments using Convolutional Neural Networks

### 2020-12-31 paper/main.tex
Add discussion on loss functions

The model is a Convolutional Neural Network based off of previous work by Q. Chen et. al.. The model takes in a visual representation of a 4096 byte chunk, that is, a 64 by 64 grayscale image. The image is then passed through a series of convolutions and max pools for feature extraction. After feature extraction, the data is passed through two 2048 classification layers ending with a softmax output\cite{chen2018}.

@@

@@

Future work could focus on developing a new purpose-built CNN. The model presented in this paper was initially built for general file fragment classification and was not adapted for compressed file fragment\cite{chen2018}. Another potential area of improvement would be exploring LSTMs. Using these networks could enable the model to learn longer distance relationships throughout the files, instead of the simpler patterns detected by CNNs\cite{LE2018S118}.

>>>>

The model is a Convolutional Neural Network based off of previous work by Q. Chen et. al.. The model takes in a visual representation of a 4096 byte chunk, that is, a 64 by 64 grayscale image. The image is then passed through a series of convolutions and max pools for feature extraction. After feature extraction, the data is passed through two 2048 classification layers ending with a softmax output. It is trained using the Adam optimizer and Sparse Categorical Crossentropy as loss function.\cite{chen2018}.

@@

Evaluating the accuracy after training the model using different optimizers and loss functions could have yielded better results.

@@

Future work could focus on developing a new purpose-built CNN. The model presented in this paper was initially built for general file fragment classification and was not adapted for compressed file fragment\cite{chen2018}. Another potential area of improvement would be exploring LSTMs. Using these networks could enable the model to learn longer distance relationships throughout the files, instead of the simpler patterns detected by CNNs\cite{LE2018S118}. Evaluating the accuracy after training the model using different optimizers and loss functions could have yielded better results. By conducting an experiment using different configurations, one could have found a better design.
